Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-09-10 source-iclr/sec_exp.tex
Update on Overleaf.

% ~\ref{th:strongcvxsmth}~\ref{th:cvxsmoth}~\ref{th:fedmasslr}
\textbf{Linear speedup of FedAvg and Nesterov accelerated FedAvg.} To verify the linear speedup convergence as shown in Theorems~\ref{thm:SGD_scvx}~\ref{thm:SGD_cvx}~\ref{thm:nesterov_scvx}~\ref{thm:Nesterov_cvx}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $\vw_0 = \textbf{0}_d$ and measure the number of iterations to reach the target accuracy $\epsilon$. For each configuration $(E, K)$, we extensively search the learning rate from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^i \ \forall i \in \ZZ$. As the results shown in Figure~\ref{fig:speedup},
the number of iterations decreases as the number of (active) workers increasing, which is consistent for FedAvg and Nesterov accelerated FedAvg across all scenarios.
For additional experiments on the impact of $E$, detailed experimental setup, and hyperparameter setting, please refer to the Appendix Section~\ref{sec:expsupp}.

>>>>

% ~\ref{th:strongcvxsmth}~\ref{th:cvxsmoth}~\ref{th:fedmasslr}
\textbf{Linear speedup of FedAvg and Nesterov accelerated FedAvg.} To verify the linear speedup convergence as shown in Theorems~\ref{thm:SGD_scvx}~\ref{thm:SGD_cvx}~\ref{thm:nesterov_scvx}~\ref{thm:Nesterov_cvx}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $\vw_0 = \textbf{0}_d$ and measure the number of iterations to reach the target accuracy $\epsilon$. For each configuration $(E, K)$, we extensively search the learning rate from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^i \ \forall i \in \ZZ$. As the results shown in Figure~\ref{fig:speedup},
sthe number of iterations decreases as the number of (active) workers increasing, which is consistent for FedAvg and Nesterov accelerated FedAvg across all scenarios.
For additional experiments on the impact of $E$, detailed experimental setup, and hyperparameter setting, please refer to the Appendix Section~\ref{sec:expsupp}.
